cardinalR: Generating interesting high-dimensional data structures

### 2025-10-03 paper-cardinalR.Rmd
Changed the order

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation")) 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T)  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

>>>>

```{r trigonometric-tb-html, eval=knitr::is_html_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", col.names = c("Function", "Explanation"), linesep = "") 
```

```{r trigonometric-tb-pdf, eval=knitr::is_latex_output()}
trigonometric_tb |> 
  kable(caption = "cardinalR trigonometric data generation functions", format="latex", col.names = c("Function", "Explanation"), booktabs = T, linesep = "")  |>
  column_spec(1, width = "4cm") |>
  column_spec(2, width = "8cm")
```

### 2025-10-03 paper-cardinalR.tex
Changed the order

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_crescent & Crescent pattern.\\
gen\_curvycylinder & Curvy cylinder.\\
gen\_sphericalspiral & Spherical spiral.\\
gen\_helicalspiral & Helical spiral.\\
gen\_conicspiral & Conic spiral.\\
\addlinespace
gen\_nonlinear & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\caption{\label{tab:trigonometric-tb-pdf}cardinalR trigonometric data generation functions}
\centering
\begin{tabular}[t]{>{\raggedright\arraybackslash}p{4cm}>{\raggedright\arraybackslash}p{8cm}}
\toprule
Function & Explanation\\
\midrule
gen\_crescent & Crescent pattern.\\
gen\_curvycylinder & Curvy cylinder.\\
gen\_sphericalspiral & Spherical spiral.\\
gen\_helicalspiral & Helical spiral.\\
gen\_conicspiral & Conic spiral.\\
gen\_nonlinear & Nonlinear hyperbola.\\
\bottomrule
\end{tabular}
\end{table}
